\documentclass[11pt, oneside, a4paper]{article}
\usepackage{graphicx} 
\usepackage[dvipsnames]{xcolor}
\usepackage[margin=20mm, top=30mm]{geometry}
\usepackage{fancyhdr}
\usepackage{tabularray}
\usepackage{tcolorbox}
\usepackage{url}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue
}
\usepackage{soul}
% Will make black underlines for links
% \hypersetup{
%   colorlinks=true,
%   linkcolor=black,
%   linkbordercolor=black,
% }
% \makeatletter
% \Hy@AtBeginDocument{%
%   \def\@pdfborder{0 0 1}
%   \def\@pdfborderstyle{/S/U/W 1}
% }
% \makeatother

\newcommand{\myboxcolor}{MidnightBlue}
\newcommand{\tipscolor}{ForestGreen}

\definecolor{mygray}{rgb}{0.92, 0.92, 0.92}


\fancypagestyle{firstpage}{
  \lhead{Editors: Junhao Zhan \& Tong Cheunchitra}
  \rhead{{Last Updated: 04/02/2025}}
}

\newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}}

\title{Getting started in Room 359}

\begin{document}

\pagestyle{fancy}
\thispagestyle{firstpage}                                      
{\centering \LARGE \textsc{Getting started in Room 359} \\}
\vspace{0.1em}

\Large
 
\begin{tcolorbox}[colback=red!5!white,colframe=red!50!white,title={Essentials!}]
    \begin{itemize}
        \item The seating plan is on the side of the bookshelf, \textbf{claim a free desk} by writing your name on the seating plan.
        \begin{itemize}
            \item Note the back two rows is reserved for PhDs
            \item Your desk is yours for your degree so feel free to personalize it and make yourself feel comfy !
        \end{itemize}
        \item Please \textbf{email Kim} at \url{kdorrell@unimelb.edu.au} and let her know 1) who you are, 2) who your supervisor is and 3) your course, so she can add you to the Astro mailing list, once you have claimed a desk.
        \item Ask for \textbf{ card access} from reception on lv 1 to get access to this room and other useful places (ask people in your group!)
        \item \textbf{Connect to the printer} via the IP address: \url{10.46.12.14} and if you \textbf{need any missing equipmet} eg. cables, cable adapters or monitors please also \textbf{email Kim} for help.
    \end{itemize}
\end{tcolorbox}
% \large
\begin{tcolorbox}[colback=\tipscolor!5!white,colframe=\tipscolor!50!white,title={Tips \& Reminders}]
    \begin{itemize}
        \item \textbf{Please lock the door} if you are the last one to leave the room, no matter what time of the day. You can lock/unlock the door by double tapping the sensor.
        \item Feel free the \textbf{check out the bookshelf}. People have worked hard to make it organized and helpful, so please, take care and return things to where they belong.
        \item The astro group has a \textbf{Slack channel}, ask you supervisor or your fellow peers in your research group to add you in.
        \item \textbf{For New Msc students}, check out this amazing GitHub by Nithin and Tong containing an unofficial guideline on the requirement of completing the research part of your degree:
        \\
        \url{https://github.com/n-babu/unimelb-astro-msc}.
        \item Katie also has a wonderful website with a bunch of useful resources related to astro for \textbf{all levels} whether you're master or PhD: 
        \\
        \url{https://sites.google.com/view/unimelb-astro-resources/home}.
        \end{itemize}
\end{tcolorbox} 

\end{document}
